### 2017-02-27 errana.tex
addressed the comments by Csaba

%!TEX root =  autocontgrlp.tex
\section{Error Analysis}\label{sec:improv}
\subsection{Properties of the Bellman Operator}
We now state without proof the most important properties of the Bellman operator(s).
The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
\begin{comment}
First, we introduce some extra notation:
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
We use $\one \in \R^n$ to denote a vector with all entries $1$.
The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
\end{comment}
\begin{lemma}\label{tprop}
\begin{enumerate}[(i)]
\item \label{monotone}$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$.
\item \label{shift}
Given $J\in \R^n$ and $t \in \R$, we have $T(J+t\one)=TJ+\alpha t\one$.
\item \label{maxnorm}
If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{shift} then
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \R^n$,
$
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
$
\item \label{uniquesol}
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{enumerate}
\end{lemma}
\begin{corollary}
If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
\end{corollary}
Though \cref{tprop} are stated for the Bellman operator $T$, the results also hold for $H$ as well.\par
We now present the analysis to derive the improved bounds where the idea is to show that the novel projection operators ($\Gamma/\hg$) are contraction maps. To this end, we go through steps similar to \Cref{tprop}-\eqref{monotone},~\eqref{shift} and ~\eqref{maxnorm}. Much the results that ensue are based on `Lyapunov' analysis where the idea is to replace the constant function $\one$ by a certain Lyapunov function (see \Cref{def:lyap}) and the $\norm{\cdot}_{\infty}$ by a weighted max-norm (see \Cref{notations}-\eqref{norms}).
\subsection{Analysis using Lyapunov Functions}
\begin{definition}\label{def:lyap}
Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
\begin{enumerate}[(i)]
\item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
\end{enumerate}
\end{definition}
\begin{assumption}\label{grlpassmp}
\begin{enumerate}[(i)]
%\item \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$.
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$.
\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
\item \label{wassmp} $W \in \R^{nd\times m}_+$ is a matrix with all positive entries.
\end{enumerate}
\end{assumption}
The error bounds for the ALP in \cite{ALP} are expressed in terms of $\frac{1}{1-\beta_{\psi}}$.  A smaller $\beta_{\psi}$ loosely implies `stability' of the the underlying MDP,  with smaller values representative of higher stability. Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov function based analysis to obtain error bounds that exploit the structure of the underlying MDP. In particular, the prior bounds suggests that the ALP is likely to generate good approximations when the underlying MDP is stable. We also adopt a similar approach by stating our results using Lyapunov function based arguments.

@@

%r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}\,.

@@

Let $r^*\eqdef\underset{r\in \R^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$, then

@@

||J^*-\Gamma J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.

@@

$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$. Then from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$. From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$. The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.

@@

\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\,\mb

@@

||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.

@@

\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\,\mb

@@

||J^*-\hv||_{\mn}
& \leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}

@@

& {}\qquad \qquad+||\Gamma J^*-\hg J^*||_{\mn}\big).

@@

||J^*-\hv||_{\mn}
& \leq ||J^*-\hg J^*||_{\mn}+||\hg J^*-\hg \hv||_{\mn}\\
&\leq ||J^*-\hg J^*||_{\mn}+\beta_\psi || J^*- \hv||_{\mn},

@@

 r'= r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.

@@

||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn
+||\Gamma J^*-\hg J^*||_{\mn}).

@@

Let $\gamma=||J^*-\Phi r^*||_{\mn}$. 

@@

||\Phi r'-J^*||_{\mn}\nn
&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\

@@

||\hj-\hv||_{1,c}
&\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\

@@

&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).\nn

@@

||J^*-\hj||_{1,c}
&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\\
&+2||\Gamma J^*-\hg J^*||_{\mn}).

@@

||J^*-\hj||_{1,c}\nn
&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn

@@

%||J_{\hu}-\hj||_{1,c}

@@

&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\mn}

@@

+||\Gamma J^*-\hg J^*||_{\mn}+||\hj-\hg\hj||_{\mn}\big).

@@

||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\,.

@@

&\leq c^\top (I-\alpha P_{\hu})^{-1} \,\psi\, ||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
%&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},

@@

&||J^*-J_{\hu}||_{1,c}\nn\\
%&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.

@@

||J^*- \hj||_{\mn}&\leq ||J^*- \hv||_{\mn}+||\hv -\hj||_{\mn}\nn

@@

The result now follows by substituting the bound on $||J^*- \hv||_{\mn}$ from \cref{cmt1mn} and the fact that $||\hv-\hj||_{\mn}\leq \frac{1}{1-\beta_{\psi}}||\hj-\hg\hj||_{\mn}$.

@@

By bounding $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ 

@@

||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}

@@

+2||J^*-\hg J^*||_{\mn}).\\

@@

||J^* - J_{\hu}||_{1,c}&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2 \,\big(10 ||J^*-\Phi r^*||_{\mn}

@@

+2||J^*-\hg J^*||_{\mn}\big).

>>>>

%!TEX root =  autocontgrlp.tex
\section{Error Analysis}\label{sec:improv}
\subsection{Properties of the Bellman Operator}
We now state without proof the most important properties of the Bellman operator(s).
The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
\begin{comment}
First, we introduce some extra notation:
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
We use $\one \in \R^n$ to denote a vector with all entries $1$.
The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
\end{comment}
\begin{lemma}\label{tprop} The following hold:
\begin{enumerate}[(i)]
\item \label{monotone}$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$.
\item \label{shift}
Given $J\in \R^n$ and $t \in \R$, we have $T(J+t\one)=TJ+\alpha t\one$.
\item \label{maxnorm}
If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{shift} then
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \R^n$,
$
\norm{TJ_1-TJ_2}_\infty\leq \alpha \norm{J_1-J_2}_\infty.
$
\item \label{uniquesol}
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{enumerate}
\end{lemma}
\begin{corollary}
If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
\end{corollary}
Though \cref{tprop} are stated for the Bellman operator $T$, the results also hold for $H$ as well.\par
We now present the analysis to derive the improved bounds where the idea is to show that the novel projection operators ($\Gamma/\hg$) are contraction maps. To this end, we go through steps similar to \Cref{tprop}-\eqref{monotone},~\eqref{shift} and ~\eqref{maxnorm}. Much the results that ensue are based on `Lyapunov' analysis where the idea is to replace the constant function $\one$ by a certain Lyapunov function (see \Cref{def:lyap}) and the $\norm{\cdot}_{\infty}$ by a weighted max-norm (see \Cref{notations}-\eqref{norms}).
\subsection{Analysis using Lyapunov Functions}
\begin{definition}\label{def:lyap}
Let $c,\rho,\chi:S \to \R_+$ be positive-valued functions. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
The function $\chi:S\to\R_+$ is a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
\end{definition}
\begin{assumption}\label{grlpassmp}
\begin{enumerate}[(i)]
%\item \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$.
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$.
\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
\item \label{wassmp} $W \in \R^{nd\times m}_+$ is a matrix with all positive entries.
\end{enumerate}
\end{assumption}
The authors of \cite{ALP} express the error bounds in terms of $\frac{1}{1-\beta_{\psi}}$.  A smaller $\beta_{\psi}$ loosely implies `stability' of the the underlying MDP,  with smaller values representative of higher stability. Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov functions based analysis to obtain error bounds that exploit the structure of the underlying MDP. In particular, the prior bounds suggests that the ALP is likely to generate good approximations when the underlying MDP is stable. We also adopt a similar approach by stating our results using Lyapunov function based arguments.

@@

%r^*\eqdef\argmin_{r\in R^k}\norm{J^*-\Phi r}_{\mn}\,.

@@

Let $r^*\eqdef\underset{r\in \R^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,

@@

\norm{J^*-\Gamma J^*}_{\mn}\leq 2 \norm{J^*-\Phi r^*}_{\mn}.

@@

$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$. Then, from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$. From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$. The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.

@@

\min_{r\in \N}\, &\norm{\Phi r-\hv}_{1,c}\,\mb

@@

\norm{\Phi r-\hv}_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.

@@

\min_{r\in \R^k}\, &\norm{\Phi r-\hv}_{1,c}\,\mb

@@

\norm{J^*-\hv}_{\mn}
& \leq \frac{1}{{1-\beta_{\psi}}}\big(2\norm{J^*-\Phi r^*}_{\mn}

@@

& {}\qquad \qquad+\norm{\Gamma J^*-\hg J^*}_{\mn}\big).

@@

\norm{J^*-\hv}_{\mn}
& \leq \norm{J^*-\hg J^*}_{\mn}+\norm{\hg J^*-\hg \hv}_{\mn}\\
&\leq \norm{J^*-\hg J^*}_{\mn}+\beta_\psi \norm{ J^*- \hv}_{\mn},

@@

r'= r+\norm{J^*-\Phi r}_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.

@@

\norm{\hj-\hv}_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4\norm{J^*-\Phi r^*}_{\mn}\nn
+\norm{\Gamma J^*-\hg J^*}_{\mn}).

@@

Let $\gamma=\norm{J^*-\Phi r^*}_{\mn}$.

@@

\norm{\Phi r'-J^*}_{\mn}\nn
&\leq \norm{\Phi r^*-J^*}_{\mn}+\norm{\Phi r'-\Phi r^*}_{\mn}\nn\\

@@

\norm{\hj-\hv}_{1,c}
&\leq\norm{\Phi \tr-\hv}_{1,c}\leq\norm{\Phi r'-\hv}_{1,c}\nn\\

@@

&\leq c^\top \psi \norm{\Phi r'-\hv}_{\mn}\nn\\
&\leq c^\top \psi (\norm{\Phi r'-J^*}_{\mn}+\norm{J^*-\hv}_{\mn}).\nn

@@

\norm{J^*-\hj}_{1,c}
&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 \norm{J^*-\Phi r^*}_{\mn}\\
&+2\norm{\Gamma J^*-\hg J^*}_{\mn}).

@@

\norm{J^*-\hj}_{1,c}\nn
&\leq\norm{J^*-\hv}_{1,c}+\norm{\hv-\hj}_{1,c}\nn\\
&\leq c^\top \psi \norm{J^*-\hv}_{\mn}+\norm{\hv-\hj}_{1,c}.\nn

@@

@@

&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2\norm{J^*-\Phi r^*}_{\mn}

@@

+\norm{\Gamma J^*-\hg J^*}_{\mn}+\norm{\hj-\hg\hj}_{\mn}\big).

@@

\norm{J^*-J_{\hu}}_{1,c}&\leq \norm{J^*-\hj}_{1,c}+\norm{J_{\hu}-\hj}_{1,c}\,.

@@

&\leq c^\top (I-\alpha P_{\hu})^{-1} \,\psi\, \norm{T\hj-\hj}_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}\norm{T\hj-\hj}_{\mn}\nn\\
%&\leq \frac{c^\top \psi}{1-\beta_{\psi}}\norm{T\hj-TJ^* +J^*- \hj}_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(\norm{T\hj-TJ^*}_{\mn} +\norm{J^*- \hj}_{\mn})\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})\norm{J^*- \hj}_{\mn},

@@

&\norm{J^*-J_{\hu}}_{1,c}\nn\\
%&\leq \norm{J^*-\hj}_{1,c}+\norm{J_{\hu}-\hj}_{1,c}\nn\\
&\leq c^\top \psi \norm{J^*-\hj}_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}\norm{J^*- \hj}_{\mn}\nn\\
&=\frac{2c^\top \psi}{1-\beta_{\psi}}\norm{J^*- \hj}_{\mn}.

@@

\norm{J^*- \hj}_{\mn}&\leq \norm{J^*- \hv}_{\mn}+\norm{\hv -\hj}_{\mn}\nn

@@

The result now follows by substituting the bound on $\norm{J^*- \hv}_{\mn}$ from \cref{cmt1mn} and the fact that $\norm{\hv-\hj}_{\mn}\leq \frac{1}{1-\beta_{\psi}}\norm{\hj-\hg\hj}_{\mn}$.

@@

By bounding $\etmn=\norm{\Gamma J^*-J^*+J^*-\hg J^*}_{\mn}\leq 2\norm{J^*-\Phi r^*}_{\mn}+\norm{J^*-\hg J^*}_{\mn}$

@@

\norm{J^*-\hj}_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 \norm{J^*-\Phi r^*}_{\mn}

@@

+2\norm{J^*-\hg J^*}_{\mn}).\\

@@

\norm{J^* - J_{\hu}}_{1,c}&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2 \,\big(10 \norm{J^*-\Phi r^*}_{\mn}

@@

+2\norm{J^*-\hg J^*}_{\mn}\big).

### 2017-02-27 intro.tex
addressed the comments by Csaba

The  framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems arising in science and engineering. By casting a given decision problem as an MDP, the goal then is to find an optimal policy ($u^*$) which is the best decision rule. The so-called dynamic programming (DP) methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states. The value function $J^*$ stands for the cumulative return of making decisions according to $u^*$. Conventional DP  techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB} can compute the exact value of $J^*$. However, a shortcoming of these conventional methods is that their computational overhead grows with the number of states, a practical hindrance when the MDP has a large number of states.\par
In this paper we consider the problem of using dynamic programming with MDPs with large state spaces. A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$. The sub-optimal policy can then be used to make the decision and results in a cumulative return given by $J_{\tu}$. The idea here is forsake optimality to gain computational tractability. The success depends on the quality of approximation, i.e., on the quantities $||J^*-\tilde{J}||$ and $\norm{J^*-J_{\tu}}$ ($\norm{\cdot}$ is an appropriate norm) known as prediction error and the control error respectively.\par

@@

\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}).
\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).

@@

A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.

@@

Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems  arising in science and engineering. In an MDP, the configuration of the system is described by the state variables (or simply the state) and the system evolves in a stochastic manner which depends on the action made. The set of all states is denoted by $S$, the state space and the set of all actions is denoted by $A$, the action space.

>>>>

The  framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems arising in science and engineering. At any decision instance, an action is made which yeilds an immediate reward and the system moves to the next state in a stochastic manner such that the next state depends only on the current state and the action chosen. The set of all states, the state space, is denoted by $S$, and the set of all actions, the action space, is denoted by $A$. Formally, a decision rule is called a policy $u$, ($u\colon S\ra A$) and has an associated value function $J_u$\footnote{Without loss of generality value function $J_u$ can be thought of as a vector in $\R^{|S|}$.}, ($J_u(s)\colon S\ra \R$) which specifies the expected cumulative reward obtained by following the policy $u$ starting from each state.\par
The so-called dynamic programming (DP) compute the optimal value function $J^*$ first and then obtain an optimal policy $u^*$ using $J^*$. Conventional DP  techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB} can compute the exact value of $J^*$ (and $u^*$). However, a shortcoming of these conventional methods is that their computational overhead grows with the number of states, a practical hindrance when the MDP has a large number of states.\par
In this paper we consider the problem of using dynamic programming with MDPs with large state spaces. A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$\footnote{It is computationally cheap to obtain such a $\tu$ from $tj$ or $u^*$ from $J^*$}. The sub-optimal policy can then be used to make the decision and results in a cumulative return given by $J_{\tu}$. The idea here is forsake optimality to gain computational tractability. The success then depends on the quality of approximation, i.e., on the quantities $\norm{J^*-\tilde{J}}$ and $\norm{J^*-J_{\tu}}$ ($\norm{\cdot}$ is an appropriate norm) known as prediction error and the control error respectively.\par

@@

\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $\norm{J^*-\hj}$ (\Cref{cmt2mn}).
\item We also bound the performance loss due to using the policy $\hu$ that is obtained using $\hj$ (Theorem~\ref{polthe}).

@@

A short and preliminary version of this paper without the theoretical analysis can be found in \cite{aaaipaper}.

@@

Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems  arising in science and engineering. In an MDP, the configuration of the system, the state, evolves in a stochastic manner in a way that the next state depends only on the last state and the action chosen. The set of all states, the state space, is denoted by $S$, and the set of all actions, the action space, is denoted by $A$.

### 2017-02-27 prob.tex
addressed the comments by Csaba

In this section, we review relevant results \cite{BertB,ALP,CS} in the linear programming approach to MDPs. Throughout the rest of the paper, we let $c>0\in \R^n$ to denote a probability distribution over the state space S.\par

@@

\textbf{Linear Programming (LP)}: It is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:

@@

\forall (s,a)\in S\times A,\nn

@@

& \Phi r\geq T \Phi r,

@@

where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP. In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}.\par

@@

\item\label{alppe} The prediction error is bounded as $||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty$.
\item\label{alpce} The control error is bounded as $||J^*-J_{\tu}||_{1,c}\leq \frac{2}{1-\alpha}||J^*-\tj||_{1,\mu_{\tu}}$.

@@

The gist of \Cref{alpvanilla}-\eqref{alppe} is that the prediction error $||J^*-\tj||_{1,c}$ of ALP is worse utmost by a constant factor than the best possible error that can be achieved using the span of $\Phi$. Further from \Cref{alpvanilla}-\eqref{alpce} the control error is worse utmost by a constant factor than the prediction error.\par

@@

||J^*-\Phi\tilde{r}_{RLP}||_{1,c}\leq ||J^*-\Phi\tilde{r}||_{1,c}+\epsilon ||J^*||_{1,c}

>>>>

In this section, we review relevant results \cite{BertB,ALP,CS} in the linear programming approach to MDPs. Throughout the rest of the paper, we let $c\in (0,1)^n$ to denote a probability distribution with strictly positive components.

@@

\textbf{Linear Programming (LP)}: As it is well known \cite{manne}, the optimal value function $J^*$ can be obtained by solving the following linear program:

@@

\forall (s,a)\in S\times A.\nn

@@

& E\Phi r\geq H \Phi r,

@@

where $E\Phi r\geq H \Phi r$ is a shorthand for the $nd$ constraints in \eqref{mdplp} which uses the definition of $H$ from \Cref{notations}-\eqref{bellactval}. Alternatively, we also use the notation $\Phi r \geq T\Phi r$, instead of $E\Phi r\geq H \Phi r$ using the definition of $T$ from \Cref{notations}-\eqref{bellopval}. Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP. In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}.\par

@@

\item\label{alppe} The prediction error is bounded as $\norm{J^*-\tj}_{1,c}\leq \frac{2}{1-\alpha}\min_{r}\norm{J^*-\Phi r}_\infty$.
\item\label{alpce} The control error is bounded as $\norm{J^*-J_{\tu}}_{1,c}\leq \frac{2}{1-\alpha}\norm{J^*-\tj}_{1,\mu_{\tu}}$.

@@

The gist of \Cref{alpvanilla}-\eqref{alppe} is that the prediction error $\norm{J^*-\tj}_{1,c}$ of ALP is worse utmost by a constant factor than the best possible error that can be achieved using the span of $\Phi$. Further from \Cref{alpvanilla}-\eqref{alpce} the control error is worse utmost by a constant factor than the prediction error.\par

@@

\norm{J^*-\Phi\tilde{r}_{RLP}}_{1,c}\leq \norm{J^*-\Phi\tilde{r}}_{1,c}+\epsilon \norm{J^*}_{1,c}
